---
title: "Package LinearRegresion"
author: "Muhammad Faizan, Fahed Maqbol, Asad Enver"
date: "September 29, 2019"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
  html_document:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r iris, include=FALSE}
data(iris)
library(linreg)
```

## Introduction
This package calculates **multiple linear regression**  for a given data set. The OOP approach used is S3 in R.
First, we calculate all the parameters we need to caclulate the required coefficients. After that, all the parameters are stored in a an object whose class is set to linreg and the function linreg returns that object. We then write methods for our class linreg to display the coefficients of our interest. 

The following functions are present in the package:

* #### linreg():
  The function **linreg()** takes two arguments formula and data and returns n object of class linreg. The object    is a list with all the required calculations necessary to perform linear regression.
    + Example:
        ``` {r res}
        res <- linreg$new(Petal.Length~Species, data = iris)
        ```
* #### print():
  The print function displays coefficients along with their names
    + Example:
        ``` {r print,message=FALSE, warning=FALSE}
        res$print()
        ```
* #### plot():
  The plot function displays two plots:
    * ##### Fitted Values v/s Residuals
    * ##### Fitted Values v/s Standardise Residulas
      > Example:
          ``` {r plot, echo=FALSE,message=FALSE, warning=FALSE}
          res$plot()
          ```
* #### resid():
  The resid function returns the vector of residuals
    + Example:
        ``` {r resid,message=FALSE, warning=FALSE}
        res$resid()
        ```
* #### pred():
  The pred function returns the predicted values ŷ
    + Example:
        ``` {r pred,message=FALSE, warning=FALSE}
        res$pred()
        ```

* #### coef():
  The coef function returns the coefficients as a named vector
    + Example:
        ``` {r coef,message=FALSE, warning=FALSE}
        res$coef()
        ```

* #### summary():
  This function presents the coefficients with their standard error, t-value and p-value as well as the estimate of   σ and the degrees of freedom in the model.

    + Example:
        ``` {r summary,message=FALSE, warning=FALSE}
        res$summary()
        ```
